### 2014-04-16 doc/uist14/iteration1.tex
iteration1: grammar/minor content updates

\section{Iteration 1: Naive IR}
\subsection{Problem Statement and Goal}
Our initial research question is: {\em Can IR-based targeting reduce the selection time compared to the case where only UI list navigation is used on a head-worn device?}

@@

\subsection{Method}
We deployed 10 wireless nodes in an indoor environment (Figure~\ref{fig:targeting-study-layout}). Each of them has a number as ID and a letter representing the name. We recruited 14 participants from our institution for this study. 13 had never used Glass before, so we offered a Google Glass tutorial before the experiment for them to get familiar with Glass gestures. Four participants wore prescription glasses, which may have affected their task performance as wearing glasses beneath Glass makes it more cumbersome to secure the position of Glass and to adjust the screen to the optimal angle. In this study, the IR LED was fixed and not repositionable as shown in Figure~\ref{fig:glass}.

@@

In the within-subject study, half of the participants performed {\em IR selection} first and the other half used {\em list selection} first. For each selection condition, we conducted 15 target selections by randomly choosing from all the targets. During the study, we measured the {\bf target acquisition time} for each target selection. Afterward, participants were asked to complete a survey of mainly open-ended answers about their experience.

@@

\begin{figure}[t]
\centering
\includegraphics[width=1.0\columnwidth]{figures/result_study1a.pdf}
\caption{Boxplot of target acquisition time for {\em IR selection} and {\em list selectioN} is shown on the left. The center of each box is the median value, while we annotate the mean value using white dashed lines.}
\label{fig:ir_vs_list}
\end{figure}

@@

To understand how scanning and refinement contribute to total selection time, we split the data from {\em IR selection} into two parts -- trials that required refinement and ones that did not. It takes 6.40 seconds (on average) to complete  a selection without any refinement, but 9.16 seconds with refinement, indicating that an additional 2.76 seconds are needed for disambiguation (see Figure~\ref{fig:with_without_refinement}). This difference is significant ($t(19)=-2.7827, p=0.012)$ using t-test.
%  \bjoern{I don't understand why we have 279 DF in the previous test but only 19 here??}). 
%% \ben{Because the times when refinement is needed is only 18 times, so the DF is bounded by the samples.}
Because many targets were spaced far apart, refinements were only necessary in 10\% of total {\em IR selection} trials in this study.

@@

In summary, {\em Naive IR} can outperform linear list selection, and most users like this head-orientation based targeting. But from our quantitative result, the refinement step detracts significantly from the efficiency of the technique.

>>>>

\section{Iteration 1: Naive IR}
Our initial research question is: {\em Can IR-based targeting reduce the selection time compared to the case where only UI list navigation is used on a head-worn device?}

@@

\subsection{Method}
We deployed 10 wireless nodes in an indoor environment (Figure~\ref{fig:targeting-study-layout}). Each of them has a number as ID and a letter representing the name. We recruited 14 participants from our institution for this study. 13 had never used Google Glass before, so we offered a tutorial before the experiment in order to introduce the device. Four participants wore prescription glasses, which makes Glass more cumbersome to use and adjust, and may have affected their task performance. In this study, the IR LED was fixed and not repositionable as shown in Figure~\ref{fig:glass}.

@@

In the within-subject study, half of the participants performed {\em IR selection} first and the other half used {\em list selection} first. For each selection condition, we conducted 15 target selections by randomly choosing from all the targets. During the study, we measured the {\bf target acquisition time} for each target selection. Afterward, participants were asked to complete a survey of primarily open-ended answers about their experience.

@@

\begin{figure}[t]
\centering
\includegraphics[width=1.0\columnwidth]{figures/result_study1a.pdf}
\caption{Boxplot of target acquisition time for {\em IR selection} and {\em list selection} is shown on the left. The center of each box is the median value, while we annotate the mean value using white dashed lines.}
\label{fig:ir_vs_list}
\end{figure}

@@

To understand how scanning and refinement contribute to total selection time, we split the data from {\em IR selection} into two parts -- trials that required refinement and ones that did not. It takes 6.40 seconds (on average) to complete  a selection without any refinement, but 9.16 seconds with refinement, indicating that an additional 2.76 seconds are needed for disambiguation (see Figure~\ref{fig:with_without_refinement}). This difference is significant $(t(19)=-2.7827, p=0.012)$ using t-test.
%  \bjoern{I don't understand why we have 279 DF in the previous test but only 19 here??}). 
%% \ben{Because the times when refinement is needed is only 18 times, so the DF is bounded by the samples.}
Because many targets were spaced far apart, refinements were only necessary in 10\% of total {\em IR selection} trials in this study.

@@

In summary, {\em Naive IR} can outperform linear list selection, and most users prefer this head-orientation based targeting. From our quantitative result, however, we foudn that the refinement step detracts significantly from the efficiency of the technique.
